### 2020-04-27 Temp_tables/Temp_tables_revision/04_city_industry/12_decile_9.tex
back up before new paper

\begin{document}% Date and time \times Sat, Apr 04, 2020 - 14:52:09
\begin{table}[!htbp] \centering 
  \caption{Decile 8} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
  output_{cit} & 0.136 & 0.137 & 0.137 & $-$0.058 & $-$0.058 & $-$0.059 \\ 
  & (0.154) & (0.154) & (0.154) & (0.114) & (0.114) & (0.114) \\ 
  capital_{cit} & 1.506$^{**}$ & 1.507$^{**}$ & 1.508$^{**}$ & 0.925$^{*}$ & 0.928$^{*}$ & 0.930$^{**}$ \\ 
  & (0.732) & (0.733) & (0.733) & (0.475) & (0.474) & (0.474) \\ 
  labour_{cit} & 3.040$^{***}$ & 3.043$^{***}$ & 3.035$^{***}$ & 1.546 & 1.545 & 1.540 \\ 
  & (0.829) & (0.832) & (0.829) & (1.019) & (1.019) & (1.018) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 8}_{i} & $-$0.306$^{**}$ & $-$0.307$^{**}$ & $-$0.308$^{**}$ & $-$0.303$^{**}$ & $-$0.323$^{**}$ & $-$0.338$^{**}$ \\ 
  & (0.122) & (0.133) & (0.134) & (0.140) & (0.149) & (0.152) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 8}_{i} \times \text{output share SOE}_{i}  & 0.723 &  &  & 1.084$^{*}$ &  &  \\ 
  & (0.548) &  &  & (0.601) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 8}_{i} \times \text{capital share SOE}_{i}  &  & 0.457 &  &  & 0.820 &  \\ 
  &  & (0.448) &  &  & (0.514) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 8}_{i} \times \text{labour share SOE}_{i}  &  &  & 0.540 &  &  & 1.046$^{*}$ \\ 
  &  &  & (0.523) &  &  & (0.594) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Year fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

>>>>

\begin{document}% Date and time \times Sun, Apr 05, 2020 - 09:43:39
\begin{table}[!htbp] \centering 
  \caption{Decile 9} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
  output_{cit} & 0.151 & 0.150 & 0.150 & $-$0.059 & $-$0.060 & $-$0.061 \\ 
  & (0.159) & (0.159) & (0.159) & (0.114) & (0.113) & (0.112) \\ 
  capital_{cit} & 1.423$^{*}$ & 1.441$^{*}$ & 1.434$^{*}$ & 0.930$^{**}$ & 0.930$^{**}$ & 0.937$^{**}$ \\ 
  & (0.736) & (0.738) & (0.736) & (0.471) & (0.471) & (0.468) \\ 
  labour_{cit} & 3.036$^{***}$ & 3.026$^{***}$ & 3.036$^{***}$ & 1.556 & 1.547 & 1.538 \\ 
  & (0.820) & (0.818) & (0.821) & (1.004) & (1.003) & (0.997) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 9}_{i} & $-$0.147 & $-$0.117 & $-$0.118 & $-$0.034 & $-$0.014 & $-$0.023 \\ 
  & (0.169) & (0.183) & (0.175) & (0.180) & (0.188) & (0.184) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 9}_{i} \times \text{output share SOE}_{ci}  & $-$0.155 &  &  & $-$0.074 &  &  \\ 
  & (0.449) &  &  & (0.499) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 9}_{i} \times \text{capital share SOE}_{ci}  &  & $-$0.214 &  &  & $-$0.146 &  \\ 
  &  & (0.420) &  &  & (0.422) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 9}_{i} \times \text{labour share SOE}_{ci}  &  &  & $-$0.246 &  &  & $-$0.110 \\ 
  &  &  & (0.453) &  &  & (0.489) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Year fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}
